---
title: "R Notebook"
output:
  html_notebook: default
  pdf_document: default
---

 
Question 1 to 4
```{r}
D=1000
K=5
h=0.05
P=2*D*K
P# saved in a variable p
l=P/h
l
Q=l^0.5# economic order quantity
Q

```

Que 1 to 4 second 
```{r}

my_vec=1:10
1+my_vec
my_vec/2


my_vec2=10:18

my_vec+my_vec2

```

```{r}
method1=seq(1,3,length=15)
method2=(1:15)
method3=c(1,2,3,4,5,6,7,8,9,0,22,222,3333,444)

method1
method2
method3





```
 in method1 we used a fn called seq that takes three parameter , first two for range and third  its length or by: division
 method2 is by using indexing it add  elements from a:b including starting and finishing  points.
 method3 is more straightforward and basic way to create a sequence
 
 
 
 
 
Q.Create a sequence of 15 numbers in all different ways and write a paragraph on the
difference between each method. 
```{r}
gl(15,2,labels = c('a','a1','a2','a3','b','b1','b2','cv','cv2','d1','d2','d3','d4','d5','d6'))
```
 
Q.  Create a Data Frame with a minimum of 5 variables and generate data for 20 observations.
The data frame should have at least a factor variable and a logical variable.
 
```{r}
 Name=c('P1','p2','p3','p4','p5','p6','p7','p8','p9','p10','p11','p12','p13','p14','p15','p16','p17','p18',"p19","p20")
Id=c(33:52)

  gender=gl(2,5,labels = c("Male","Female"))
   Weight=round(seq(55,99,length=20),0)
  Height=round(seq(148,170,length=20),0)
  Age=round(seq(16,33,length=20),0)
  You_are_a_student=c(T,F,T,F,T,T,F,T,T,F,T,F,T,T,T,F,F,F,T,F)

dataf=data.frame(Name,Id,gender,Weight,Height,Age,You_are_a_student)
dataf 
```
 Q.Write a R program to call the (built-in) dataset mtcars. 
```{r}

mtcars

```
 
 Q.Order the entire data frame by the first and second column.
 
 
```{r}
ordered_df=dataf[order(dataf$Name,dataf$Id),]

ordered_df
```
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 
 