---
title: "LAB-3"
output: html_notebook
---

1. What is the sum of the first 100 positive integers? The formula for the sum of
integers 1 through n. n is n(n+1)/2n(n+1)/2.
Define n=100n=100 and then use R to compute the sum of 11 through 100100 using the
formula. What is the sum?
```{r}
n=100

summation=n*(n+1)/2
summation
```
2. Now use the same formula to compute the sum of the integers from 1 through 1,000.


```{r}
k=1000
sum1000=k*(k+1)/2
sum1000

```
3. Look at the result of typing the following code into R:
n <- 1000
x <- seq(1, n)
sum(x)
Based on the result, what do you think the functions seq and sum do? You can use help.
a. sum creates a list of numbers and seq adds them up.
b. seq creates a list of numbers and sum adds them up.
c. seq creates a random list and sum computes the sum of 1 through 1,000.
d. sum always returns the same number.


```{r}
n = 1000
x= seq(1, n)
sum(x)

class(x)

x # its not random


```
ANSWER:   seq creates a list of numbers and sum adds them up.

4. In math and programming, we say that we evaluate a function when we replace the
argument with a given number. So if we type sqrt(4), we evaluate the sqrt function. In R, you
can evaluate a function inside another function. The evaluations happen from the inside out.
Use one line of code to compute the log, in base 10, of the square root of 100.



```{r}
log10(sqrt(100))


```

5. Which of the following will always return the numeric value stored in x? You can try out
examples and use the help system if you want.
a. log(10^x)
b. log10(x^10)
c. log(exp(x))
d. exp(log(x, base = 2))


```{r}
x=1
log(10^x)
log10(x^10)
log(exp(x))
exp(log(x, base = 2))


```
ANSWER: 
c. log(exp(x))
d. exp(log(x, base = 2))


6. Load the US murders dataset.
install.packages(“dslabs”)
library(dslabs)
data(murders)
Use the function str to examine the structure of the murders object. Which of the following
best describes the variables represented in this data frame?
a. The 51 states.
b. The murder rates for all 50 states and DC.
c. The state name, the abbreviation of the state name, the state’s region, and the state’s
population and total number of murders for 2010.

d. str shows no relevant information.
2. What are the column names used by the data frame for these five variables?
3. Use the accessor $ to extract the state abbreviations and assign them to the object a. What is
the class of this object?
4. Now use the square brackets to extract the state abbreviations and assign them to the
object b. Use the identical function to determine if a and b are the same.
5. We saw that the region column stores a factor. You can corroborate this by typing:
class(murders$region)
With one line of code, use the function levels and length to determine the number of regions
defined by this dataset.





```{r}

library(dslabs)
data(murders)

murders
str(murders)


#answer
#c. The state name, the abbreviation of the state name, the state’s region, and the state’s
#population and total number of murders for 2010.


```


6.2 What are the column names used by the data frame for these five variables?


```{r}

names(murders)
```


6.3. Use the accessor $ to extract the state abbreviations and assign them to the object a. What is
the class of this object?


```{r}

a=murders$abb


class(a)
```


6.4. Now use the square brackets to extract the state abbreviations and assign them to the
object b. Use the identical function to determine if a and b are the same.

```{r}

b=murders[,2]
b

identical(a,b)
```

6.5. We saw that the region column stores a factor. You can corroborate this by typing:
class(murders$region)
With one line of code, use the function levels and length to determine the number of regions
defined by this dataset.




```{r}
murders$region

length(levels(murders$region))

```











